\documentclass[draftmode]{main}

\begin{document}

% ____________________________________________________________________________
% Title page
\begin{center}
\Large Diss. ETH No. 26027
\end{center}

\vspace{3cm}
\begin{center}
\huge
Measurement and interpretation of differential cross sections for Higgs boson production
\\
and
\\
determination of the strong coupling constant $\alphas$ using measurements of the top-antitop quark pair production cross section\par
\end{center}

\vspace{1cm}
\begin{center}
\large
A thesis submitted to attain the degree of \\
Doctor of Sciences of ETH Zurich (Dr. sc. ETH Zurich)
\end{center}

\vspace{1cm}
\begin{center}
\large
Presented by \\[10pt]
{\huge Thomas Klijnsma} \\[10pt]
MSc. Physics, ETH Zurich \\
Born on May 28th, 1991 \\
Citizen of the Netherlands\par
\end{center}

\vspace{1cm}
\begin{center}
\large
Accepted on the recommendation of \\[5pt]
Prof. Dr. G{\"u}nther Dissertori, examiner \\
Prof. Dr. Rainer Wallny, co-examiner \\
Dr. Gavin P. Salam, co-examiner\par
\end{center}

\vspace{1cm}
\begin{center}
\large
% \today
2019
\end{center}

\thispagestyle{empty} % No page number
\null\newpage\thispagestyle{empty}\null % Empty page after title page
% ____________________________________________________________________________


\import{tex/}{numbers}
\import{tex/}{abstract}
\import{tex/}{abstract_german}

\tableofcontents

\import{tex/}{introduction}
\import{tex/}{theory}
\import{tex/}{detector}

\import{tex/}{inputs}
\import{tex/differentials/}{differentials}
\import{tex/interpretation/}{interpretation}
\import{tex/}{projections}
\import{tex/alphas/}{alphas}

\import{tex/}{summary}

\bibliographystyle{cmsbibstyle}
\bibliography{bibs/references,bibs/alphas}

\appendix
\import{tex/}{appendix_theory}
\import{tex/}{appendix_regression}
\import{tex/differentials/}{appendix}
\import{tex/differentials/}{regularization}
\import{tex/alphas/}{appendix}

\import{tex/}{acknowledgments}

\end{document}