\section{Including strongly correlated uncertainty sources in the combination}
\label{sec:appendix}

Our approach of excluding strongly correlated uncertainties from the combination is generally recommended when using the covariance matrix to fit strongly correlated data~\cite{DAgostini:1993arp}.
% 
To illustrate the effect of strong correlations, the combination is here performed again with the PDF, scale and $\mt$ uncertainties included in the combination one by one.
% 
The PDF and scale uncertainties are considered fully correlated between measurements made with the LHC, and partially correlated between measurements made with the LHC and Tevatron.
% 
In the case of the PDF uncertainties the degree of correlation between LHC and Tevatron measurements was determined using the procedure described in Ref.~\cite{Buckley:2014ana}.
%
The $\mt$ uncertainties are considered fully correlated for all measurements.
% 

Tables~\ref{tab:theoryUncertainties_CT14_NNLO} and \ref{tab:theoryUncertainties_CT14_NNLO_NNLL} show the results for the CT14 PDF set, using NNLO and NNLO+NNLL respectively, and Tables~\ref{tab:theoryUncertainties_NNPDF30_NNLO} and \ref{tab:theoryUncertainties_NNPDF30_NNLO_NNLL} for the NNPDF30\_nolhc PDF set.
% 
As expected, the total uncertainty decreases as more sources are included in the combination.
% 
As the sensitivity to $\as$ is stronger for a larger cross section, determinations that deviate up can have a smaller uncertainty, and therefore obtain a larger weight in the combination.
% 
This is the case for the determination from the ATLAS measurement at 7$\TeV$ when using the CT14 PDF set.
% 
A larger weight may also be obtained for determinations that are more independent with respect to the others. This is primarily the case for the Tevatron determination, for both PDF sets.
% 
These effects are enhanced if the overall correlation is increased by including strongly correlated uncertainty sources, which explains why the combination yields increasing values of $\as$ as more sources are included.
% 
The results found this way are larger than both the straight average and the median of the individual determinations, though the difference is well within one standard deviation. 
% 
Taking them as our final results would imply a high degree of trust in the assumed correlations.
% 
Due to the inherent difficulty of determining correlations, notably as concerns the scale variations, and the importance of the subtle interplay between an individual determination's $\alpha_s$ result and its error, the conservative approach is to exclude the strongly correlated sources from the combination.
%

\begin{table}[ht] 
\renewcommand{\arraystretch}{1.4}
\setlength\tabcolsep{5pt}
\centering
{\scriptsize
    % \begin{center} 
    \hspace*{-0.75cm}%
    \begin{minipage}[b]{0.5\hsize}\centering
    \topcaption{
        Combination results including also uncertainties from the PDF, the scale
        and the top mass in the combination.
        % 
        The first row corresponds to our
        approach of excluding correlated uncertainties from the combination.
        % 
        The results listed here are obtained using NNLO cross sections with
        the CT14nnlo series of PDFs.
        }
    \label{tab:theoryUncertainties_CT14_NNLO}
    \begin{tabular}{l l l l}
    \toprule
    \lcell{2.4cm}{Uncertainties included in combination} & 
    \lcell{0.7cm}{Center} & 
    \lcell{1.5cm}{Combination uncertainty} & 
    \lcell{1.5cm}{Total uncertainty} \\ 
    \midrule
    \input{img/alphas/extr-NNLO-CT14nnlo_theoryUncertaintyEffect.tex}
    \bottomrule
    \end{tabular} 
    \end{minipage}%
    % 
    \hspace*{1cm}%
    % 
    \begin{minipage}[b]{0.5\hsize}\centering
    \topcaption{%
        As in Table~\ref{tab:theoryUncertainties_CT14_NNLO}, but now using NNLO+NNLL
        cross sections with the CT14nnlo series of PDFs.
        }
    \label{tab:theoryUncertainties_CT14_NNLO_NNLL}
    \begin{tabular}{l l l l }
    \toprule
    \lcell{2.4cm}{Uncertainties included in combination} & 
    \lcell{0.7cm}{Center} & 
    \lcell{1.5cm}{Combination uncertainty} & 
    \lcell{1.5cm}{Total uncertainty} \\ 
    \midrule
    \input{img/alphas/extr-NNLO-NNLL-CT14nnlo_theoryUncertaintyEffect.tex}
    \bottomrule
    \end{tabular} 
    \end{minipage}
    % 
    % NEW LINE
    \\[16pt]
    % 
    \hspace*{-0.75cm}%
    \begin{minipage}[b]{0.5\hsize}\centering
    \topcaption{%
        As in Table~\ref{tab:theoryUncertainties_CT14_NNLO}, but now using NNLO
        cross sections with the NNPDF30\_nolhc series of PDFs.
        }
    \label{tab:theoryUncertainties_NNPDF30_NNLO}
    \begin{tabular}{l l l l }
    \toprule
    \lcell{2.4cm}{Uncertainties included in combination} & 
    \lcell{0.7cm}{Center} & 
    \lcell{1.5cm}{Combination uncertainty} & 
    \lcell{1.5cm}{Total uncertainty} \\ 
    \midrule
    \input{img/alphas/extr-NNLO-NNPDF30-nolhc-nnlo_theoryUncertaintyEffect.tex}
    \bottomrule
    \end{tabular} 
    \end{minipage}%
    % 
    \hspace*{1cm}%
    % 
    % \begin{center} 
    % \hspace*{-0.75cm}%
    \begin{minipage}[b]{0.5\hsize}\centering
    \topcaption{
        As in Table~\ref{tab:theoryUncertainties_CT14_NNLO}, but now using NNLO+NNLL
        cross sections with the NNPDF30\_nolhc series of PDFs.
        }
    \label{tab:theoryUncertainties_NNPDF30_NNLO_NNLL}
    \begin{tabular}{l l l l }
    \toprule
    \lcell{2.4cm}{Uncertainties included in combination} & 
    \lcell{0.7cm}{Center} & 
    \lcell{1.5cm}{Combination uncertainty} & 
    \lcell{1.5cm}{Total uncertainty} \\ 
    \midrule
    \input{img/alphas/extr-NNLO-NNLL-NNPDF30-nolhc-nnlo_theoryUncertaintyEffect.tex}
    \bottomrule
    \end{tabular} 
    \end{minipage}%
}%
\end{table} 


% ____________________________________________________________________________
\section{Overview of asymmetric uncertainties used in the combination}
\label{sec:appendix2}

Tables~\ref{tab:uncertaintyCoefficients_CT14_NNLO} and \ref{tab:uncertaintyCoefficients_CT14_NNLO_NNLL} show the numerical values for the uncertainty coefficients used in the combination procedure for the CT14 PDF set, using NNLO and NNLO+NNLL cross sections respectively.
% 
Only experimental uncertainties are listed.
% 
Theoretical uncertainties, which are taken into account after the combination procedure, can be found in Tables~\ref{tab:determination_NNLO_CT14}-\ref{tab:determination_NNLO_NNLL_NNPDF30nolhc}.
% 
The correlations for the correlated uncertainties (with a $\delta$ symbol) are described in Section~\ref{sec:correlationcoefficients}.

\begin{table}[ht] 
\renewcommand{\arraystretch}{2.0}
\providecommand{\ErrTableWidth}{1.0cm}
\setlength\tabcolsep{5pt}
\centering
{\footnotesize
    \hspace*{-0.75cm}%
    \begin{minipage}[b]{0.5\hsize}\centering
        \topcaption{%
            Overview of the uncertainty coefficients for the CT14 (NNLO) PDF set.
            % 
            The coefficients with a $\delta$ correspond to the coefficients of the correlated
            uncertainty sources, and those with a $\Delta$ to the uncorrelated uncertainty sources.
            }
        \label{tab:uncertaintyCoefficients_CT14_NNLO}
        \begin{tabular}{l c c c c c }
        \toprule
        \input{img/alphas/extr-Oct16-NNLO-CT14nnlo_all_deltas.tex}
        \bottomrule
        \end{tabular} 
        \end{minipage}%
    % 
    \hspace*{1cm}%
    % 
    \begin{minipage}[b]{0.5\hsize}\centering
        \topcaption{%
            As in Table~\ref{tab:uncertaintyCoefficients_CT14_NNLO}, but now using
            NNLO+NNLL cross sections with the CT14 PDF set.
            }
        \label{tab:uncertaintyCoefficients_CT14_NNLO_NNLL}
        \begin{tabular}{l c c c c c }
        \toprule
        \input{img/alphas/extr-Oct16-NNLO-NNLL-CT14nnlo_all_deltas.tex}
        \bottomrule
        \end{tabular} 
        \end{minipage}%    % 
}%
\end{table} 

